Quality Definitions of Qualities

### 2021-10-09 StateOfPractice/QDefOfQualities/QDefOfQualities.tex
added traceability definitions

>>>>

\begin{defn}
This is the property of a system description technique which allows changes in one of the three system descriptions -- requirements, specification, implementation -- to be traced to the corresponding portions of the other descriptions. The correspondence should be maintained throughout the lifetime of the system \citep{greenspan1978structuring}.
\end{defn}

\begin{defn}
The ability to relate requirements specifications with other artefacts created
in the development life-cycle of a software system \citep{spanoudakis2002plausible}.
\end{defn}

\begin{defn}
Symbol identification that permits symbols to be traced throughout a software system. Also, continuity between program versions \citep{graf1999modern}.
\end{defn}
